---
title: "graphic_description"
description: |
  Comparisons of weight and height between men and women
author:
  - name: Louanne Degallaix
    url: {}
date: 11-14-2020
categories :
  - "Data Sciences I"
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
SciViews::R
```

```{r}
data <- read("biometry", package = "BioDataScience")
```

We want to analyse human biometry to compare men's and women's height and weight. The measurement was produced between 2013 and 2014 on people from different ages. 

```{r}
a <- chart(data, weight ~ gender %fill=% gender) +
  geom_boxplot(show.legend = FALSE)

b <- chart(data, height ~ gender %fill=% gender) +
  geom_boxplot(show.legend = FALSE)

combine_charts(list(a, b))
```

On the graphic A, we can see that men are heavier than women in general. Indeed 75% women weigh less than about 70 kg in comparison 50% men weigh more than 70kg. 

On the graphic B, we can see that men are taller than women. Indeed 75% women measure less than 170 cm and 75% men measure more than 170cm.

